|

### 2017-11-16 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Revisions towards the final version

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
library(igraph)
library(ggplot2)
library(ggraph)
library(stringr)
library(scales)
library(textreuse)
source("../R/helper.R")
source("../R/section-matches.R")
source("../R/spectrogram.R")
load("../cache/corpus-lsh.rda")
load("../cache/network-graphs.rda")
set.seed(82893)
```

*This article is currently under peer review at the American Historical Review.*

@@

```{r code-to-code-network, fig.width=6.5, fig.height=7, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure. Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code. States that adopted any of the variations on the Field Code became part of a network centered on New York capital."} 
set.seed(3728)
ggraph(codes_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                               angle = 15)) + 
  geom_node_point(aes(color = as.factor(distance)), size = 5) +   
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") +    
  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +   
  scale_color_discrete("Distance from a Field Code") +
  ggforce::theme_no_axes() +  
  geom_node_text(aes(label = name), size = 3, family = "Palatino") +
  labs(title = "The migration of the Field Code",
       subtitle = "Codes of civil procedure connected by borrowed sections") +
  theme(legend.position = "bottom",
        panel.border = element_blank(),
        text = element_text(family = "Palatino"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        plot.title = element_text(face = "bold"))
```

@@

```{r ca1850-borrowings, fig.height=3, fig.align="center"}
spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
                                                   "NY1848"), base_size = 10)
```

@@

```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
spectrogram("CA1851", best_matches, white_list = 3, base_size = 10)
```

@@

```{r WA1855-borrowings, fig.height=4.5, fig.align="center"}
spectrogram("WA1855", best_matches, white_list = c("CA1850", "CA1851", "IN1852",
                                                   "NY1853", "OR1854", "WI1849"),
            base_size = 10)
```

@@

```{r WA1873-borrowings, fig.height=4.5, fig.align="center"}
spectrogram("WA1873", best_matches, base_size = 10)
```

>>>>

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
library(igraph)
library(ggplot2)
library(ggraph)
library(stringr)
library(scales)
library(textreuse)
source("../R/helper.R")
source("../R/section-matches.R")
source("../R/spectrogram.R")
load("../cache/corpus-lsh.rda")
load("../cache/network-graphs.rda")
set.seed(82893)
dir.create("../out/figures", recursive = TRUE, showWarnings = FALSE)
bw <- TRUE
```

@@

```{r code-to-code-network, fig.width=17.5, fig.height=12.5, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure. Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code. States that adopted any of the variations on the Field Code became part of a network centered on New York capital."} 
set.seed(3728)
network_g <- ggraph(codes_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                               angle = 15)) +
  geom_node_point(aes(color = as.factor(distance)), size = 6) +   
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") +    
  scale_edge_alpha(range = c(0.5, 0.5), guide = "none") +   
  scale_color_manual(name = "Distance from a Field Code",
                     values = c("0" = "#ff0000",
                                "1" = "#1d91c0",
                                "2" = "#41b6c4",
                                "3" = "#7fcdbb",
                                "4" = "#c7e9b4",
                                "5" = "#edf8b1",
                                "6" = "#ffffd9",
                                "Inf" = "#dfc27d")) +
  ggforce::theme_no_axes() +  
  geom_node_text(aes(label = name), size = 5, family = "Palatino") +
  labs(title = "The migration of the Field Code",
       subtitle = "Codes of civil procedure connected by borrowed sections") +
  theme(legend.position = "bottom",
        panel.border = element_blank(),
        text = element_text(family = "Palatino"),
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 15),
        plot.title = element_text(size = 22, face = "bold"),
        plot.subtitle = element_text(size = 18))
print(network_g)
ggsave("../out/figures/figure-05.svg", network_g, width = 17.5, height = 12.25)
ggsave("../out/figures/figure-05.pdf", network_g, width = 17.5, height = 12.25)
ggsave("../out/figures/figure-05.png", network_g, width = 17.5, height = 12.25)
```

@@

```{r CA1850-borrowings, fig.height=3, fig.align="center"}
spec_CA1850 <- spectrogram("CA1850", best_matches, 
                           white_list = c("LA1844", "NY1829", "NY1849", "NY1848"),
                           base_size = 10)
spec_CA1850_bw <- spectrogram("CA1850", best_matches, 
                              white_list = c("LA1844", "NY1829", "NY1849", "NY1848"),
                              base_size = 10, bw = TRUE)
if (!bw) {
  print(spec_CA1850) 
} else {
  print(spec_CA1850_bw)
} 
ggsave("../out/figures/figure-06.svg", spec_CA1850, width = 7, height = 3)
ggsave("../out/figures/figure-06.pdf", spec_CA1850, width = 7, height = 3)
ggsave("../out/figures/figure-06.png", spec_CA1850, width = 7, height = 3)
ggsave("../out/figures/figure-06-bw.svg", spec_CA1850_bw, width = 7, height = 3)
ggsave("../out/figures/figure-06-bw.pdf", spec_CA1850_bw, width = 7, height = 3)
ggsave("../out/figures/figure-06-bw.png", spec_CA1850_bw, width = 7, height = 3)
```

@@

```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
spec_CA1851 <- spectrogram("CA1851", best_matches, 
                           white_list = 3, base_size = 10)
spec_CA1851_bw <- spectrogram("CA1851", best_matches, 
                              white_list = 3, base_size = 10, bw = TRUE)
if (!bw) {
  print(spec_CA1851) 
} else {
  print(spec_CA1851_bw)
} 
ggsave("../out/figures/figure-07.svg", spec_CA1851, width = 7, height = 3.5)
ggsave("../out/figures/figure-07.pdf", spec_CA1851, width = 7, height = 3.5)
ggsave("../out/figures/figure-07.png", spec_CA1851, width = 7, height = 3.5)
ggsave("../out/figures/figure-07-bw.svg", spec_CA1851_bw, width = 7, height = 3.5)
ggsave("../out/figures/figure-07-bw.pdf", spec_CA1851_bw, width = 7, height = 3.5)
ggsave("../out/figures/figure-07-bw.png", spec_CA1851_bw, width = 7, height = 3.5)
```

@@

```{r WA1855-borrowings, fig.height=4.5, fig.align="center"}
spec_WA1855 <- spectrogram("WA1855", best_matches, 
                           white_list = c("CA1850", "CA1851", "IN1852", 
                                          "OR1854"),
                           base_size = 10)
spec_WA1855_bw <- spectrogram("WA1855", best_matches, 
                              white_list = c("CA1850", "CA1851", "IN1852", 
                                             "OR1854"),
                              base_size = 10, bw = TRUE)
if (!bw) {
  print(spec_WA1855) 
} else {
  print(spec_WA1855_bw)
} 
ggsave("../out/figures/figure-08.svg", spec_WA1855, width = 7, height = 4.5)
ggsave("../out/figures/figure-08.pdf", spec_WA1855, width = 7, height = 4.5)
ggsave("../out/figures/figure-08.png", spec_WA1855, width = 7, height = 4.5)
ggsave("../out/figures/figure-08-bw.svg", spec_WA1855_bw, width = 7, height = 4.5)
ggsave("../out/figures/figure-08-bw.pdf", spec_WA1855_bw, width = 7, height = 4.5)
ggsave("../out/figures/figure-08-bw.png", spec_WA1855_bw, width = 7, height = 4.5)
```

@@

```{r WA1873-borrowings, fig.height=4.5, fig.align="center"}
spec_WA1873 <- spectrogram("WA1873", 
                           white_list = c("CA1872", "IN1852", "WA1855"),
                           best_matches, base_size = 10)
spec_WA1873_bw <- spectrogram("WA1873", best_matches,
                              white_list = c("CA1872", "IN1852", "WA1855"),
                              base_size = 10, bw = TRUE)
if (!bw) {
  print(spec_WA1873) 
} else {
  print(spec_WA1873_bw)
} 
ggsave("../out/figures/figure-09.svg", spec_WA1873, width = 7, height = 4.5)
ggsave("../out/figures/figure-09.pdf", spec_WA1873, width = 7, height = 4.5)
ggsave("../out/figures/figure-09.png", spec_WA1873, width = 7, height = 4.5)
ggsave("../out/figures/figure-09-bw.svg", spec_WA1873_bw, width = 7, height = 4.5)
ggsave("../out/figures/figure-09-bw.pdf", spec_WA1873_bw, width = 7, height = 4.5)
ggsave("../out/figures/figure-09-bw.png", spec_WA1873_bw, width = 7, height = 4.5)
```
